### 2016-06-02 doc/seminario-arqsw/presentation/src/arqsw-paper-presentation.tex
Modificações na pd

\section{Conclusions}
\begin{frame}{Conclusions}
	\begin{itemize}
		\item he HDFS Committers appear to maintain intellectual control over their code base. They can do this because the code base is not very large and because they are a relatively small, stable, and co-located group. Therefore, the architecture documentation did not interest or affect the Committers (as measured by their response to our surveys and their lack of referring to it in the JIRA postings and mail archives).
		The HDFS community of Committers (and the most active Contributors) is actively interested in architectural concepts, as shown by the text analysis that we did. They frequently discuss architectural concepts, but this architectural information is implicitly shared, and informally presented and disseminated, dispersed in mail archives and JIRA postings.
		The architecture documentation that we created did appear to have an effect on the project, but principally on “outsiders,” such as, less active Contributors, and newcomers. Many people accessed the documentation web pages (over 25,000 to date) and there were many return visitors (33 percent, more than 8,000, of the page visits were return visits).
		The project's social network became less centralized and the speed of promotion from Commenter to Contributor was (statistically significantly) quicker after the introduction of the documentation. Newcomers are not participating more (in terms of volume of contributions), but they are becoming more effective. This is, of course, correlation, and does not prove causation. While the lessening of centralization and increasing promotion rates are consistent with the claimed effects of explicit architectural documentation, there may be other explanations for both phenomena.
		The architecture documentation did not appear to significantly affect submission activity or quality. There was more activity after the introduction of the architecture documentation, but this may have been due to confounding factors
	\end{itemize}

@@

\section{Threats to Validity}
\begin{frame}{Threats to Validity}
	\begin{itemize}
	    \item

>>>>

\section{Conclusions}
\begin{frame}{Conclusions}
	\begin{itemize}
		\item The HDFS Committers appear to maintain intellectual control over their code base.
		\item The HDFS community of Committers and the most active Contributors is actively interested in architectural concepts.
	\end{itemize}

@@

\begin{frame}{Conclusions}
	\begin{itemize}
		\item The architecture documentation  to have an effect on the project, but principally on less active Contributors and newcomers.
		\item The project's social network became less centralized and the speed of promotion from Commenter to Contributor was quicker after the introduction of the documentation.
	\end{itemize}

\section{Threats to Validity}
\begin{frame}{Threats to Validity}
	\begin{itemize}
	     \item The findings must be intended as observed correlations, whose causal linkage to architectural documentation still remains to be explored and validated
             \item :
	\end{itemize}
